---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# {{cookiecutter.project_name}}

<!-- badges: start -->
<!-- badges: end -->

This R-package contains an app about {{cookiecutter.project_name}}.

{{cookiecutter.description}}


## Installation

If you would like to run the app locally on your PC, you can install the {{cookiecutter.package_name}} package as

``` r
require("devtools")
devtools::install_github("{{cookiecutter.github_name}}/{{cookiecutter.package_name}}")
```

## Example

After installion you can start the app in this package as follows:

```{r example, eval=FALSE}
library({{ cookiecutter.package_name }})
run_app()
```

## Project organisatie

```
├── app.R                               <- Script to start the app properly on shinyapps.io
├── data-raw                            <- Scripts create the datasets
├── DESCRIPTION                         <- Project description
├── inst
│   ├── dashboard
│   │   ├── data                        <- Folder containing the datasets for the dashboard or app
│   │   └── www                         <- Folder with style-files, javascript and favicon
│   └── extdata                         <- Folder extra data to be included in the package
├── LICENSE.md                          <- License
├── man                                 <- Help-files with explanation on the available functions
│   └── run_app.Rd
├── NAMESPACE
├── NEWS.md                             <- File containing news on the package such as new features in the latest version
├── R                                
│   └── run_app.R                       <- Main function that starts the app
├── README.md
├── README.Rmd                          <- README with explanation and description of the project
└── {{cookiecutter.package_name}}.Rproj
```

--------

<p><small>Project based on the <a target="_blank" href="https://github.com/reidhin/cookiecutter/tree/main/Rshiny_package">cookiecutter R-shiny package template</a></small></p>

